
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 15: Writing a function - Conditional Statement"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment15.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------
###titanic data set
#### NOTICE: Question 7, 8 and 9 are optional. 

-------
1. Write a function to calculate the age of a person.  Give an example to test your function. 

- Input: a number, x, (year born)

- Output: Print out "You are r age". Where r is the age of the person, i.e. 2020 - x. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#42)
```{r}
birth <- function(x)
{
  r = (x)
  print(paste0("You are " , r, " age"))
}
```

```{r}
birth(15)
```
-------

2. Write the following function. Give an example to test your function. 

- Input: a number

- Output: print out: "You input an even number!" if the number is event, or "You input an odd number!" otherwise. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#46)
```{r}
number <- function(x)
{
  if (x %% 2 == 0)
  {
    print("You input an even number!")
  } 
  else
  {
    print("You input an odd number!")
  }
}
```

```{r}
number(2)
number(3)
```

-------

3. Write the following function.  Give an example to test your function. 

- Input: a numeric vector 

- Output:  

  - if the input vector has missing values: return the input vector with missing values replaced by mean
  
  - if the input vector has no missing value: return the same input vector
  
Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#50)
```{r}
mode_impute <- function(x)
{
  if(!is.numeric(x))
  {
    mode_of_x <- names(sort(-table(x)))[1]
    library(tidyr)
    x <- replace_na(x, mode_of_x) 
  }
return(x)    
}
```

```{r}
library(tidyverse)
df <- read_csv('WHO-COVID-19-global-data.csv')
x1 <- mode_impute(df$Cumulative_cases)
sum(is.na(x1))
```

-------

4. Write the following function.  Give an example to test your function. 

- Input: a vector x 

- Output:  The vector x where the missing values replaced by the mean (if x is numeric) or the mode (if x is non-numeric).  If x does not have missing value, return the same vector x.  

Hint: Use If-statement to combine the function in Question 3 and [this function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#49)
```{r}
impute_missing <- function(x) 
  {
  if (anyNA(x)) 
  {
  if (is.numeric(x)) 
  {
      x[is.na(x)] <- mean(x, na.rm = TRUE)
  } 
  else 
  {
      mode_of_x <- names(sort(-table(x)))[1]
      x[is.na(x)] <- mode_of_x
  }
}
  return(x)
}

```

```{r}
library(tidyverse)
df <- read_csv('WHO-COVID-19-global-data.csv')
x1 <- mode_impute(df$Cumulative_cases)
sum(is.na(x1))
```
-------

5. Write the following function. Give examples to test your function. 

- Input: A data frame of two variables x and y

- Output: 

  - A boxplot of x by y if x is numeric and y is non-numeric
 
  - A boxplot of y by x if y is numeric and x is non-numeric
 
  - print out 'This function cannot visualize your data' otherwise

Hint: 

- [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#53)
 
- You can refer to this slide to plot a boxplot: https://bryantstats.github.io/math421/slides/6_viz.html#36

```{r}
viz <- function(d)
{
  if(is.numeric(d[[1]])&is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[1]], y = d[[2]]))+
      geom_boxplot()+
      labs(x = names(d)[1], y = names(d)[2])
  }
  else if (!(is.numeric(d[[1]])|is.numeric(d[[2]])))
  {
    d %>% ggplot(aes(x = d[[1]], fill = d[[2]]))+
      geom_boxplot(position = 'dodge')+
      labs(x = names(d)[1], fill = names(d)[2])
  }
  else 
  {
    print('This function cannot visualize your data.')
  }
}
```


```{r}
d <- df %>% select(Date_reported, Cumulative_deaths)
viz(d)
```
 
-------
 
6. Combine the function in Question 5 and the function in this example ([Link](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#53)) to have a function that can plot all possible cases (2 categorical, 2 numeric, 1 numeric and 1 categorical). 
```{r}
impute_missing <- function(x) {
  if (anyNA(x)) {
    if (is.numeric(x)) {
      x[is.na(x)] <- mean(x, na.rm = TRUE)
    } else {
      mode_of_x <- names(sort(-table(x)))[1]
      x[is.na(x)] <- mode_of_x
    }
  }
  return(x)
}

plot_data <- function(data, x_var, y_var, group_var = NULL, type = "scatter") {
  data[[x_var]] <- impute_missing(data[[x_var]])
  data[[y_var]] <- impute_missing(data[[y_var]])

  if (type == "scatter") {
    if (!is.null(group_var)) {
      ggplot(data, aes_string(x = x_var, y = y_var, color = group_var)) +
        geom_point() +
        labs(x = x_var, y = y_var, color = group_var) +
        ggtitle("Scatter Plot")
    } else {
      ggplot(data, aes_string(x = x_var, y = y_var)) +
        geom_point() +
        labs(x = x_var, y = y_var) +
        ggtitle("Scatter Plot")
    }
  } else if (type == "bar") {
    if (!is.null(group_var)) {
      ggplot(data, aes_string(x = x_var, fill = group_var)) +
        geom_bar() +
        labs(x = x_var, fill = group_var) +
        ggtitle("Bar Plot")
    } else {
      ggplot(data, aes_string(x = x_var)) +
        geom_bar() +
        labs(x = x_var) +
        ggtitle("Bar Plot")
    }
  } else {
    print("Invalid plot type. Choose 'scatter' or 'bar'.")
  }
}

```

-------

#### NOTICE: Question 7, 8 and 9 are optional. 

-------

7. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the accuracy of the decision model `rpart` where the training data is train_percent. 

-------

8. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the plot of variable important by random forest trained by caret. 


---
9. Write the following function. Give examples to test your function. 

- Input: 

  - a data frame that has a text column 
  
  - the name of the text column in the data

- Output: the word cloud plot of the text column

Sample codes

- [Word Cloud codes](https://bryantstats.github.io/math421/assignments/text_mining_sample_codes2.html#Total_Word_Cloud)

- [A similar function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#10)


