
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14 - Extra: Networks of Words"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment14_extra.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE)
```

-------

Following [this document](https://www.tidytextmining.com/nasa) to plot a network of words for one of the text datasets.
```{r}
library(RedditExtractoR) 
library(tidytext)
library(ggpubr) 
library(tidyverse) 
library(knitr)
library(lubridate)
```

```{r, eval=FALSE}
df1 <- find_thread_urls(sort_by="new", subreddit = 'work')
```
```{r, eval=FALSE}
write_csv(df1, "reddit_work.csv")
```

```{r}
df1 = read_csv("reddit_work.csv")
```


```{r}
library(igraph)
library(ggraph)
library(dplyr)
library(widyr)
library(tidytext)
keyword_pairs <- df1 %>% 
  pairwise_count(date_utc, title, sort = TRUE, upper = FALSE)

keyword_pairs
set.seed(1234)
graph <- keyword_pairs %>%
  filter(n >= 1) %>%
  graph_from_data_frame(directed = TRUE)

ggraph(graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "royalblue") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()

```

