
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 16: Writing a function - Loop"
---
```{r}
library(tidyverse)
library(purrr)
```


```{r}
df <- read_csv('titanic.csv')
```

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment16.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

1. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of numeric variables replaced by the associated means.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)

```{r}
for (i in df)
{ 
  print(sum(is.na(i)))
}
```
```{r}
for (i in 1:length(df))
{
  print(class(df[[i]]))
}
```

```{r}
mean1 <- function(x)
{
  if(is.numeric(x))
  {
    mean2 <- mean(x, na.rm = TRUE)
    library(tidyr)
    x <- replace_na(x, mean2) 
  }
return(x)    
}
```


```{r}
numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
      d[[i]] <- mean1(d[[i]])
  }
  return(d)
}
```

```{r}
colSums(is.na(df))
```

```{r}
d1 <- numeric_impute(df)
colSums(is.na(d1))
```

-------

2. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of variables replaced by the associated means (for numeric variables) or modes (for non-numeric variables).

Hint: Use If-statement to combine the function in Problem 1 and the function in [this example](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)

```{r}
mean_mode <- function(x)
{
  if(is.numeric(x))
  {
    mean2 <- mean(x, na.rm = TRUE)
    library(tidyr)
    x <- replace_na(x, mean2) 
  }
  
  if(!is.numeric(x))
  {
    # Find the mode of x
    mode_of_x <- names(sort(-table(x)))[1]
    # Replace the missing by the mode
    library(tidyr)
    x <- replace_na(x, mode_of_x) 
  }
  
return(x)    
}


impute2 <- function(d)
{
  for (i in 1:length(d))
  {
      d[[i]] <- mean_mode(d[[i]])
  }
  return(d)
}
```

```{r}
colSums(is.na(df))
```
```{r}
d1 <- impute2(df)
colSums(is.na(d1))
```

-------

3. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: Bar plots of all non-numeric variables

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#33)
```{r}
density_plot <- function(d)
{
  library(ggplot2)
  for (i in 1:length(d))
  {
    if (!is.numeric(d[[i]]))
    {
      print(ggplot(d, aes(x = d[[i]]))+ 
              geom_bar()+
              labs(x = names(d)[i]))
    }
  }
}
```

```{r}
density_plot(df)
```

-------

4. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: all possible the bar plots of a non-numeric variable filled by a non-numeric variable.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40)

```{r}
density_plot2 <- function(d)
{
  library(ggplot2)
  
  l <- length(d)
  
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_density()+labs(x = names(d)[i], color = names(d)[j]))
    }
  }
}
```

-------

5. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: 

  - all possible the bar plots of a non-numeric variable filled by a non-numeric variable.
  
  - all possible the density plots of a numeric variable colored by a non-numeric variable
  
  - all possible the scatter plots.

Hint: Combine [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#37), [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40), and the function in Question 4. One way to combine is creating a new function, `quick_plot`, and call these three functions within `quick_plot`. 
```{r}

```


