
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Data Wrangging with `dplyr`"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 4. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### 1. Install `tidyverse` package

An R package can be installed by `install.packages` function. Install `tidyverse` if you have not done so. 

```{r}
library(tidyverse)
```

-------

#### 2. Read the data using `read_csv`

Use `read_csv` function to import the US Covid 19 data at [link](https://covidtracking.com/data/download/all-states-history.csv).  Don't forget to import `tidyverse` (library(tidyverse)) so that you can use read_csv. 
```{r}
df <- read_csv('https://covidtracking.com/data/download/all-states-history.csv') 

```
```{r}
names(df)
```

-------

#### 3.  Fix the date and ceate some new variables

`lubridate` is a package of the `tidyverse` packages.  We will make uses of `lubridate` in this question.

- Use the below codes to create `month`, `weekday` and `monthday` variables

```{r}
library(lubridate)

df <- df%>%
  mutate(month = months(date),
       weekday = wday(date),
       monthday = mday(date))

```

-------

#### 4. Create new variables with `case_when`. 

The function `case_when` is a good option to create a new variable from existing variable.  For example, this below codes create a new variable, `daily_death`, from `deathIncrease` variable.  `deathIncrease` is the number of daily new death by Covid19.  The new variable `daily_death` takes three values:  low (if `deathIncrease` less than 3), medium (`deathIncrease` from 3 to 14), and high (`deathIncrease` more than 14).  Please notice that this can also be done in a different way as shown in Assignment 3. 

```{r}
df <- df %>% 
mutate(daily_death = case_when(
  df$deathIncrease < 3 ~ 'low',
  df$deathIncrease >= 3 & df$deathIncrease <= 14 ~ 'medium',
  TRUE ~'high'))
```

- Create variable `month2` that takes three values: early_month (day of the month from 1-10), mid_month (day of the month from 11-20), and end_month (day of the month > 20).
```{r}
#df <- data.frame(day = c(1:31))

df$month2 <- case_when(
  df$monthday <= 10 ~ "early_month",
  df$monthday > 10 & df$monthday <= 20 ~ "mid_month",
  df$monthday > 20 ~ "end_month"
)
print(df)
```

- Create variable `weekend` that takes two values:  1 if it's Saturday or Sunday or 0 otherwise. 


```{r}
df <- df %>%
  mutate(weekend = ifelse(wday(date) %in% c(6, 7), 1, 0))
  
```

-------

#### 5. Select function

Use the select function to deselect the column `totalTestsViral` from the data.
```{r}
df %>% select(-totalTestsViral)
```

-------

#### 6. Pipe Operator ( %>% )

Pipe operator offers another way to write R codes. Many times, it makes the codes more readable.  Pipe works very well with all the `tidyverse` packages. Refer to [these slides](../slides/4_dplyr.html#15) (slide 15, 16, 17 and 18) to rewrite the below codes using pipe operator

```{r}
x <- c(1:10)
result <- x %>%
  sqrt() %>%
  sum() %>%
  
sum(x) 
### pipe
x %>% sum

# square root of x
sqrt(x)
x %>% sqrt

sqrt(sum(x))
x %>% sum %>% sqrt
#
sum(sqrt(x))
x %>% sqrt %>% sum

log(sum(sqrt(x)))
log(sum(x))


# log base 2 of 16
log(16, 2)

```

-------

#### 7. Combo 1: group_by + summarise

This combo is used when you want to apply a function/calculation to different groups of the data. For example, to calculate the average number of cases (`positiveIncrease`) by `dataQualityGrade`, we use:

```{r}
df %>% 
  group_by(weekday) %>% ##change date to weekday at some point
  summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `month`
```{r}
df %>% 
  group_by(month2) %>%
  summarise(median(positiveIncrease))
```


- Calculate the average number of cases (`positiveIncrease`) by `month2`
```{r}
df%>%
  group_by(month2) %>%
  summarise(mean(positiveIncrease))

```

- Calculate the median number of cases (`positiveIncrease`) by `weekend`
```{r}
df %>%
  group_by(weekend) %>%
  summarise(median(positiveIncrease))

```


-------

#### 8. Combo 2: filter + group_by + summarise

An example: to calculate the average number of cases (`positiveIncrease`) in January and February separately, we use:

```{r}
df %>% 
  filter(month == 'January'| month == 'February') %>% 
  summarise(positve_increase = mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) on the weekend by `month` in October and November 2020. 
```{r}
df %>% 
  filter(month == 'October'|month== 'November') %>% 
  group_by(2020) %>% 
  summarise(positve_increase = median(positiveIncrease))
```

- Calculate the average number of death at different periods of a month (`month2` variable) in Fall 2020
```{r}
df %>% 
  filter(month == 'October'| month == 'November' | month == 'December') %>% 
  group_by(2020) %>% 
  summarise(number_of_deaths = mean(death))
```

- Compare the average number of hospitalizations between weekdays and weekends in Summer 2020


- Redo Questions 14 and 15 in [Assignment 3](assignment3.html) using the combos.  Notice:  you also need to use the data used in Assignment 3.  

-------

#### 9. Combo 3: filter + group_by + summarise + arrange

Use the arrange function to find a month that has the highest number of deaths on the weekend. 


-------

#### 10. Use your own dataset and implement the follows functions or combos. You can use the [Adult Census Income](../data/adult_census.csv) or [Titanic data](../data/titanic.csv). 
```{r}
df <- read_csv('adult_census.csv')
```

- select
- filter
- mutate
- summarise
- arrange
- count
- count + arrange
- filter + count + arrange
- group_by + summarise
- filter + group_by + summarise
- filter + group_by + summarise + arrange